---
title: "Class notes 9.29"
author: Andrew Gard
format: html
embed-resources: true
---

```{r}
#| label: setup
#| message: false

library(tidyverse)
```

## Missing data

Broadly speaking, there are three kinds of missing data.

1) **Missing completely at random**, where a random sample of observations are deleted or missing. This is how `slice_sample` works. When doing plots or models, R and other languages assume this type.

2) **Missing at random**, where there are correlations with other variables, but still randonimity in the missingness. It's sometimes possible to *impute* the missing values in this situation.

3) **Missing not at random**, where there are real-world reasons for missing data that may not be apparent from the spreadsheet.

## Example: the `msleep` set.

```{r}
glimpse(msleep)
```

Let's start by looking at conservation status. We can learn about the abbreviations used on the internet. What about the `NA`s for this variable? Let's start by isolating these observations.

```{r}
conserv_na <- msleep %>% 
  filter(is.na(conservation))

gt::gt(conserv_na)
```

Some googling tells us that these species weren't endangered at the time the set was made. These `NA`s aren't random. They mean something. We could replace these `NA`s with "not endangered" or something. A useful command is `tidyr::replace_na`.

What about `sleep_rem`? Is the missingness of this variable related to other variables in the set? We might try to answer this by making some plots where missingness is a variable. Let's just check vs `vore`. Ideally, you should check vs every variable of interest in your analysis.

```{r}
#| fig-alt: a bar chart showing missingness broken down by vore. Carnivores are more likely to be missing, omnivores less. 

msleep <- msleep %>% 
  mutate(sleep_rem_na = is.na(sleep_rem))

ggplot(msleep, aes(x = vore, 
                   fill = sleep_rem_na)) +
  geom_bar(position = "fill") +
  scale_fill_brewer(palette = "Dark2")
```

If we drop observations with missing `sleep_rem`, we'll disproportionately be dropping carnivores, which probably isn't great.






