---
title: "Class notes template"
format: html
embed-resources: true
---

```{r}
#| label: setup
#| message: false

library(tidyverse)
library(readxl)

color_survey <- read_csv("color_survey.csv")

```

## A bit about hex codes for colors

The first row in the `color_survey` set has color `#4864af`. What does this mean? We read this in pairs, giving us red, green, and blue components. Here, 48 red. These values are in *hexadecimal*, or just *hex*, which means they're base 16.

The hex number 48 means 4 sixteens and 8 ones. This is 16*4 + 8 = 72. 

What about the blue component, af? In hex, a is 10, b is 11 etc., so af is 10 sixteens and 15 ones. This is 175 in decimal.

You don't want to use hex code and RGB - they carry the same information. The RGB is dissecting that number.

If you put the color code in a code chunk, RStudio will show it to you. Nicola's github for examples. 

```{r}
"#4864af"
```



```{r}
billboard_long %>% 
  head(10) %>% 
  gt::gt()
```

Problem 2
```{r}
speeds_long %>% 
  group_by(`AIRPORT CODE`) %>% 
  filter(Speed == max(speed)) %>% 
  ungroup() %>% 
  count(Carrier) %>% 
  arrange(-n) %>% 
  gt()


