---
title: "Moyo_Inference_HW6"
author: "Kyle Moyo"
format: html
editor: visual
embed-resources: true
---

```{r}
#| label: setup
#| message: false
#| error: false

library(tidyverse)
library(ISLR2)
```

Let's take a look at the dataset and store the data we want in a variable (`Price` in `Carseats`.)

```{r}
glimpse(Carseats)

```

## Problem 1

Do the prices in the dataset `Carseats`provide evidence against the company’s claim that the average price of their own seats is \$110?

In this case, we test the following hypothesis:

$$
\begin{aligned}
H_0 &: \mu = 110 \\
H_1 &: \mu \neq 110
\end{aligned}
$$

Let's visualize the data using a histogram to get a sense of the how the prices of `Carseats` vary. We can see that the values are distributed normally with a slight left skew.

```{r}
#| fig-alt: A histogram visualizing the spread of carseat prices. Prices are distributed roughly normally, with a slight left skew. 
#| message: false

Carseats %>%
  ggplot(aes(x = Price)) +
           geom_histogram () +
           labs(title = "Prices of Carseats",
                x = "Price",
                y = "Count") +
  theme_minimal()
)
  
  
```

Now that we have these, we can compute a test-statistic for our sample. We only have the sample mean, so the t-test (two-sided) is the preferred method.

```{r}
t.test(Carseats$Price, mu = 110)
```

Since p \< $\alpha = 0.05$ we reject the null hypothesis and conclude that the company's claim is fairly accurate. The average price of their seats is indeed \$110.

## Problem 2

We are computing a 90% confidence interval for `CompPrice` in `Carseats`.

```{r}
t.test(Carseats$CompPrice, conf.level = .90)
```

As we can seen see, the computed sample mean is `124.975`. To determine the margin of error, we can subtract the upper and lower bounds shown above.

```{r}
126.2391 -  123.7109
```

$\bar{x} = 124.975$ME = 2.5282\$

## Problem 3

```{r}
t <- table(penguins$species, penguins$island)
addmargins(t)

counts
```
